\textit{Supplementary materials for}: Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-10-24 paper/supplement.tex
finished a round of edits to the supplement

    1     &     FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice? &                                           Neither you nor your computer has enough mass to cause a noticable gravitational attraction &                You and your computer are too close for the gravitational attraction to be significant &                                                                        Humans are too small to detect the force of gravity &  The gravitational attraction between you and your computer is disrupted by the larger gravitational field generated by the earth \\\hline

@@

5  &          FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar... \\\hline
6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...\newline\textbf{[06:37.31--07:28.1]} ...that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in... \\\hline

@@

11 &          FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Ullom charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar... \\\hline

@@

\caption{\textbf{Lecture-specific questions and lecture excerpts.} We used the
text embeddings of each question about \textit{Four Fundamental Forces} (FFF)
and \textit{Birth of Stars} to identify corresponding matching intervals of the
lectures. The text of the questions and the best-matching time intervals of the
lecture transcripts are displayed (lecture times are noted in square brackets).
Timecourses of topic correlations for each question may be found in
Supplemntary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
no matching lecture interval was found for Question 29.} 
\label{tab:matches}
\end{longtable}
\end{tiny}

@@

    \caption{\textbf{Topic correlation timeseries plots for individual
    \textit{Four Fundamental Forces} questions}. Each panel displays a
    timeseries plot showing how the question's topic vector correlates with the
    topic vectors for each timepoint of \textit{Four Fundamental Forces}. The
    shaded regions in each curve denote the full width at half maximum (FWHM)
    of the peak(s) in the curve. These FWHM intervals were used to identify the
    corresponding lecture intervals displayed in Supplementary
    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
    (local maxima) within each shaded region.}
    \label{fig:forces-peaks}
\end{figure}

@@

    \caption{\textbf{Topic correlation timeseries plots for individual
    \textit{Birth of Stars} questions}. Each panel displays a
    timeseries plot showing how the question's topic vector correlates with the
    topic vectors for each timepoint of \textit{Birth of Stars}. The
    shaded regions in each curve denote the full width at half maximum (FWHM)
    of the peak(s) in the curve. These FWHM intervals were used to identify the
    corresponding lecture intervals displayed in Supplementary
    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
    (local maxima) within each shaded region.}

@@

    \caption{\textbf{Topic correlations versus word overlap}. \textbf{A.
    Single-timepoint comparisons for \textit{Four Fundamental Forces}.} Each
    question about \textit{Four Fundamental Forces} was compared to each
    timepoint of the lecture (dots). The blue dots denote the correlations
    between the topic vectors, and the orange dots denote Jaccard similarities
    (defined as the number of unique words in common between the question and
    corresponding window of the lecture, divided by the total number of unique
    words in both). \textbf{B. Single-timepoint comparisons for \textit{Birth
    of Stars}. Same format as Panel A. \textbf{C. Topic correlation timeseries
    plots.} This panel is in the same format as Figure 4A from the main text,
    but here the example question highlighted in purple in Panel A has been
    emphasized for the \textit{Four Fundamental Forces} traces on the left, and
    the example question highlighted in green in Panel B has been emphasized
    for the \textbf{Birth of Stars} traces on the right. \textbf{D. Jaccard
    similarity timeseries plots.} These panels are in the same format as Panel
    C, but they display the Jaccard similarity timeseries for the same
    questions. \textbf{E. Question and lecture text.} The text for the example
    purple (left) and green (right) questions is shown on top, and the text
    from the best-matching intervals of the lectures (computed using topic
    correlations; see Supp. Tab.~\ref{tab:matches}) are shown on the bottom.}}

@@

    \caption{\textbf{Comparing LDA vs. BERT embeddings}. The rows of the
    display the equivalents of Figures 2C (top row), 4A and B (middle two
    rows), and 3B (bottom row) computed using LDA (left) and BERT (right).}

>>>>

    1     &     FFF &                                                                                                                                                                                   Why is the gravitational attraction between you and your computer too small for you to notice? &                                           Neither you nor your computer has enough mass to cause a noticeable gravitational attraction &                You and your computer are too close for the gravitational attraction to be significant &                                                                        Humans are too small to detect the force of gravity &  The gravitational attraction between you and your computer is disrupted by the larger gravitational field generated by the earth \\\hline

@@

5  &          FFF &                                                                                                                                                                                            Which of the following is a difference between gravity and the electromagnetic force? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar... \\\hline
6  &          FFF &                                                                                                                                                                                                  Electricity and magnetism can be shown to be two cases of the same force if we: &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar...\newline\textbf{[06:37.31--07:28.1]} ...that the cool force the electrostatic force and the magnetic force are actually the same thing viewed in different frames of references so I won't go into a lot of detail but just keep that in the back of your mind that they are connected in a future video I'll go more into the intuition of how they are connected and it deals with when what it's more apparent when they're moving when the charges are moving at relativistic frames and you have well I will go to a lot of detail there but just keep in mind that they really are the same force just viewed from different frames of reference now the strongest of the force is probably the best name of them all and that's the strong force that is the strong force the strong force and although you probably haven't seen this yet in our in chemistry classes it actually applies very strongly in... \\\hline

@@

11 &          FFF &                                                                                                                                                                                                                          Which force is stronger than the Electromagnetic Force? &                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  \textbf{[04:34.28--05:52.61]} ...times the strength of gravity 10 to 36 times the strength of gravity so it kind of puts the weak force in its place it's 10 to the 12 times stronger than the weak force so these are huge numbers that we're talking about either this relative that or even this relative to gravity and so you might be saying well you know the electromagnetic force that's unbelievably strong why doesn't that apply over over over these these kind of macro scales like gravity let me write there macro scales macro scales why doesn't it apply to macro scales and actually there's nothing about the electromagnetic force why it can't it or it actually does apply over large distances the reality though is you don't have these huge concentrations of either electric Coulomb charges or magnetism the way you do mass so the mass that you have such huge concentrations it can operate over huge huge distances even though it's way way way weaker than the electromagnetic force the electromagnetic force what happens is because it's both attractive and repulsive it tends to kind of sort itself out so you don't have these huge huge huge concentrations of charge now the other thing you might be wondering about is you know why is it called the electromagnetic force in our everyday life there's things like there's things like the Coulomb force that or the electrostatic force which we're familiar... \\\hline

@@

\caption{\textbf{Lecture-specific questions and lecture excerpts.} We used the
text embeddings of each question about \textit{Four Fundamental Forces} (FFF)
and \textit{Birth of Stars} to identify corresponding matching intervals of the
lectures. The text of the questions and the best-matching time intervals of the
lecture transcripts are displayed (lecture times are noted in square brackets).
Time courses of topic correlations for each question may be found in
Supplemntary Figures~\ref{fig:forces-peaks} and~\ref{fig:bos-peaks}. Note that
no matching lecture interval was found for Question 29.} 
\label{tab:matches}
\end{longtable}
\end{tiny}

@@

    \caption{\textbf{Topic correlation time series plots for individual
    \textit{Four Fundamental Forces} questions}. Each panel displays a
    time series plot showing how the question's topic vector correlates with the
    topic vectors for each timepoint of \textit{Four Fundamental Forces}. The
    shaded regions in each curve denote the full width at half maxima (FWHM)
    of the peak(s) in the curve. These FWHM intervals were used to identify the
    corresponding lecture intervals displayed in Supplementary
    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
    (local maxima) within each shaded region.}
    \label{fig:forces-peaks}
\end{figure}

@@

    \caption{\textbf{Topic correlation time series plots for individual
    \textit{Birth of Stars} questions}. Each panel displays a
    time series plot showing how the question's topic vector correlates with the
    topic vectors for each timepoint of \textit{Birth of Stars}. The
    shaded regions in each curve denote the full width at half maxima (FWHM)
    of the peak(s) in the curve. These FWHM intervals were used to identify the
    corresponding lecture intervals displayed in Supplementary
    Table~\ref{tab:matches}. The diamonds denote the peak correlation values
    (local maxima) within each shaded region.}

@@

    \caption{\textbf{Topic correlations versus word overlap}. \textbf{A.
    Single-timepoint comparisons for \textit{Four Fundamental Forces}.} Each
    question about \textit{Four Fundamental Forces} was compared to each
    timepoint of the lecture (dots). The blue dots denote the correlations
    between the topic vectors, and the orange dots denote Jaccard similarities
    (defined as the number of unique words in common between the question and
    corresponding window of the lecture, divided by the total number of unique
    words in both). \textbf{B. Single-timepoint comparisons for \textit{Birth
    of Stars}}. Same format as Panel A. \textbf{C. Topic correlation time series
    plots.} This panel is in the same format as Figure 4A from the main text,
    but here the example question highlighted in purple in Panel A has been
    emphasized for the \textit{Four Fundamental Forces} traces on the left, and
    the example question highlighted in green in Panel B has been emphasized
    for the \textit{Birth of Stars} traces on the right. \textbf{D. Jaccard
    similarity time series plots.} These panels are in the same format as Panel
    C, but they display the Jaccard similarity time series for the same
    questions. \textbf{E. Question and lecture text.} The text for the example
    purple (left) and green (right) questions is shown on top, and the text
    from the best-matching intervals of the lectures (computed using topic
    correlations; see Supp.~Tab.~\ref{tab:matches}) are shown on the bottom.}

@@

    \caption{\textbf{Comparing LDA vs. BERT embeddings}. The rows display the
    equivalents of main text Figure 2C (top row), Figures 4A and 4B (middle two
    rows), and Figure 3B (bottom row) computed using LDA (left) and BERT
    (right).}
